### Modelado Bayesiano.

```{r}
brm_subject_formula <- Response ~ 1 + (1 | Subject)
```

```{r}
#| cache: true
brm_subject <-
    brm(
        brm_subject_formula,
        data = df_clean,
        family = cumulative("logit"),
        sample_prior = TRUE,
        file = "models/brm_subject",
        file_refit = "on_change"
    )
```


```{r}
prior_draws(brm_subject) %>%
pivot_longer(cols = everything(), names_to = "term", values_to = "value") %>%
    ot(aes(x = value, y = term, fill = term)) +
  ge_violin() +
labs(y = NULL) +
    t_wrap(~term, scales = "free_x") +
   cd_cartesian(xlim = c(-15, 15)) +
 thee(legend.position = "none") +
  adfacet_borders()
```

```{r}
tibble(theta = seq(-10, 10)) %>%
 mut(p = inv_logit_scaled(theta)) %>%
gplo(aes(x = theta, y = p)) +
om_line(size = 1)
```

```{r}
plot(brm_subject, ask = FALSE,
     variable = "^b_|^sd_", regex = TRUE)
``

```{r}
brm_subject
```

```{r}
# label: tbl-comp-1
# tbl-cap: Comparación de los coeficientes del modelo clmm y brm Response ~ 1 + (1 | Subject)
clmm_subject$coef %>%  as_tibble %>% mutate(term = str_c("b_Intercept[", 1:4, "]")) %>%  
    bind_rows(tibble(value=attr(VarCorr(clmm_subject)$Subject, "stddev"), term="sd_Subject__Intercept")) %>% 
      janitor::clean_names() %>% 
      left_join( 
        broom.mixed::tidyMCMC(brm_subject), 
        by = "term" 
      ) %>% 
      relocate(term) %>% 
      rename(ordinal.clmm=value, brms.brm=estimate) %>% mutate(across(where(is.numeric), ~round(., 2))) %>% 
       select(-std.error) %>% gt 
```

```{r}
#| echo: true
#| cache: true
brm_treat.period_subject_question <- brm(
    Response ~ Treat * Period + (1 | Subject) + (1 | Question),
    data = df_clean,
    family = cumulative("logit"),
    sample_prior = TRUE,
    file = "models/brm_treat.period_subject_question",
    file_refit = "on_change"
)
summary(brm_treat.period_subject_question)
```


```{r}
#| echo: true
#| cache: true
brm_treat.period.subject.question <- brm(
    Response ~ Treat * Period + (1 + Treat | Subject) + (1 + Treat | Question),
    data = df_clean,
    family = cumulative("logit"),
    sample_prior = TRUE,
    file = "models/brm_treat.period.subject.question",
    file_refit = "on_change"
)
summary(brm_treat.period.subject.question)
```

```{r}
#| echo: true
#| cache: true
brm_cs.treat.subject.question <- brm(
    Response ~ 1 + cs(Treat) + (1 | Subject) + (1 | Question),
    data = df_clean,
    family = cumulative("logit"),
    sample_prior = TRUE,
    file = "models/brm_cs.treat.subject.question",
    file_refit = "on_change"
)
summary(brm_cs.treat.subject.question)
```

```{r}
#| echo: true
#| cache: true
brm_treat_question_subject <- brm(
    Response ~ 1 + Treat + (1 | Question) + (1|Subject),
    data = df_clean,
    family = cumulative("logit"),
    sample_prior = TRUE,
    file = "models/brm_treat_question_subject",
    file_refit = "on_change"
)
summary(brm_treat_question_subject)
```


```{r}
LOO(
  brm_subject,
  brm_treat.period_subject_question,
  brm_treat.period.subject.question,
  brm_cs.treat.subject.question
)
```

```{r}
conditions <- make_conditions(brm_treat.period_subject_question, vars = c("Treat", "Question"))
conditional_effects(brm_treat.period_subject_question,  categorical=T, conditions=conditions, re_formula=NULL, ask=F, robust=T,  prob=0.5)
```

```{r}
#| echo: true
#| cache: true
brm_treat_question_subject_question <- brm(
    Response ~ 1 + Treat + (1 | Question) + (1|Subject:Question),
    data = df_clean,
    family = cumulative("logit"),
    sample_prior = TRUE,
    file = "models/brm_treat_question_subject_question",
    file_refit = "on_change"
)
summary(brm_treat_question_subject_question)
```
